Leveraging the VTA-TVM Hardware-Software Stack \\for FPGA Acceleration of 8-bit ResNet-18 Inference

### 2018-06-11 dissemination.publication/9375838469ad4029/paper.tex
final meta updates
added instructions how to use CK snapshot from ACM DL

\begin{itemize}
  \item {\bf Algorithm:} Deep Learning, Neural Networks, ResNet-18 inference, 2D convolutions
  \item {\bf Program:} MxNet
  \item {\bf Compilation:} NNVM, TVM
  \item {\bf Transformations:} TVM Schedule Optimizations, loop splitting, loop reordering, tensorization, virtual threading
  \item {\bf Binary:} FPGA bit-stream and RPC server executable
  \item {\bf Data set:} ImageNet 2012 validation (50,000 images) and ResNet-18 8-bit
  \item {\bf Run-time environment:} Ubuntu 15.04; Python2/3
  \item {\bf Hardware:} Xilinx Pynq-Z1 FPGA development board, x86 host desktop/laptop
  \item {\bf Run-time state:} 100MHz clock, 2W SoC peak consumption
  \item {\bf Execution:} remote execution via RPC
  \item {\bf Metrics:} total execution time; top1/top5 accuracy over some (all) images from the data set
  \item {\bf Output:} classification result; execution time; accuracy
  \item {\bf Experiments:} automated via CK command line
  \item {\bf How much disk space required (approximately)?:} 200MB for VTA repo
  \item {\bf How much time is needed to prepare workflow (approximately)?:} 15 mins for inference only, 2 hours for hardware compilation of hardware artifact
  \item {\bf How much time is needed to complete experiments (approximately)?:} 20 mins for full Imagenet test dataset
  \item {\bf Publicly available?:} Will be (not at the time of the publishing)
  \item {\bf Code license?:} 
  \item {\bf Collective Knowledge workflow framework used?:} Yes
  \item {\bf CK workflow URL:} \url{https://github.com/ctuning/ck-request-asplos18-resnet-tvm-fpga}
  \item {\bf CK results URL:} \url{https://github.com/ctuning/ck-request-asplos18-results-resnet-tvm-fpga}
  \item {\bf Original artifact URL:} \url{https://github.com/uwsaml/vta}
\end{itemize}

@@

>>>>

\begin{itemize}
  \item {\bf Algorithm:} Deep Learning, Neural Networks, ResNet-18 inference, 2D convolutions
  \item {\bf Program:} MxNet
  \item {\bf Compilation:} NNVM, TVM
  \item {\bf Transformations:} TVM Schedule Optimizations, loop splitting, loop reordering, tensorization, virtual threading
  \item {\bf Binary:} FPGA bit-stream and RPC server executable
  \item {\bf Data set:} ImageNet 2012 validation (50,000 images) and ResNet-18 8-bit
  \item {\bf Run-time environment:} Ubuntu 15.04; Python2/3
  \item {\bf Hardware:} Xilinx Pynq-Z1 FPGA development board, x86 host desktop/laptop
  \item {\bf Run-time state:} 100MHz clock, 2W SoC peak consumption
  \item {\bf Execution:} remote execution via RPC
  \item {\bf Metrics:} total execution time; top1/top5 accuracy over some (all) images from the data set
  \item {\bf Output:} classification result; execution time; accuracy
  \item {\bf Experiments:} automated via CK command line
  \item {\bf How much disk space required (approximately)?:} 200MB for VTA repo
  \item {\bf How much time is needed to prepare workflow (approximately)?:} 15 mins for inference only, 2 hours for hardware compilation of hardware artifact
  \item {\bf How much time is needed to complete experiments (approximately)?:} 20 mins for full Imagenet test dataset
  \item {\bf Publicly available?:} Will be (not at the time of the publishing)
  \item {\bf Code license?:} Apache 2.0
  \item {\bf Collective Knowledge workflow framework used?:} Yes
  \item {\bf CK workflow URL:} \url{https://github.com/ctuning/ck-request-asplos18-resnet-tvm-fpga}
  \item {\bf CK results URL:} \url{https://github.com/ctuning/ck-request-asplos18-results-resnet-tvm-fpga}
  \item {\bf Original artifact URL:} \url{https://github.com/uwsaml/vta}
\end{itemize}

@@

\subsubsection{Install this CK workflow from the ACM Digital Library snapshot}

It is possible to install and test the snapshot of this workflow 
from the ACM Digital Library without interfering with your current CK installation.
Download related file "request-asplos18-artifact-?-ck-workflow.zip"
to a temporary directory, unzip it and then execute the following commands:

\begin{verbatim}
$ . ./prepare_virtual_ck.sh
$ . ./start_virtual_ck.sh
\end{verbatim}

All CK repositories will be installed in your current directory.
You can now proceed with further evaluation as described below.
